### 2018-10-01 ms.tex
Rewrite abstract.

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
malaria is bad but decreasing
moving to strategy of elimination country by country
elimination requires maps of low prevalence areas
but maps in low prevalence areas are difficult
sometimes little data
traditional prevalence mapping won't work
we need new sources of data.

>>>>

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
As malaria incidence decreases and more contries move towards elimination, maps of malaria risk in low prevalence areas are becoming increasingly needed.
However, traditional mapping using prevalence point-surveys are often ineffective in low prevalence areas due to low statistical power and a lack of data.
Therefore, models must be developed that can estimate risk at high spatial resolution from surveillance data that reports incidence aggregated to a geographic polygon.
Current models formulated for polygon incidence data suffer from lower statistical power for learning relationships between malaria risk and environmental covariates.
Here we present a joint model that uses both polygon incidence and prevalence point-surveys.
